Overlapping Batches for the Assessment of Solution Quality in Stochastic Programs

### 2014-06-09 Referee2_Response.tex

\begin{itemize}
\item[] \textit{4, 54 (and elsewhere): When you refer to ``variable amounts of overlap'', that is really nothing new. Certainly, any overlapping estimator will have end effects in which the overlap amounts differ from those in the ``middle'' region of the data.}
\end{itemize}

\noi
You are right.
We meant to say that the degree of overlap is parametrized and this parameter can be chosen by the user. 
We reworded this sentence to reflect this. 
xxxx  We also \ldots (I think we should write more about our conclusions and our recommendation based on our new findings here) xxxx
\medskip

\begin{itemize}
\item[] \textit{4, 57 (and elsewhere): ``classical case'' refers to nonoverlapping batch means, right?}
\end{itemize}

\noi
No; by `classical case', we meant the use of overlapping batches in simulation output analysis (as opposed to the assessment of solution quality in stochastic programming). 
We reworded this sentence to make it clear. 
Please note that based on your earlier comments, we also reworded this sentence to avoid using the term `variance reduction'. 
\medskip

@@

\begin{itemize}
\item[] \textit{5, 14: ``realization of the univariate stochastic''}
\end{itemize}

\noi
Done.  
\medskip

\begin{itemize}
\item[] \textit{5, 35 (and elsewhere): Careful! This isn't quite the sample variance! This is actually the sample variance multiplied by $m/n$.}
\end{itemize}

\noi
Thanks for catching this. 
We corrected this sentence. 
Please note that we broke this sentence into two to avoid long sentences and to improve exposition. 
We also checked for other occurrences of the term `sample variance' throughout the paper and corrected these terms as well. 
\medskip

@@

\begin{itemize}
\item[] \textit{5, 43: You could have introduced the notation ``CI'' earlier.}
\end{itemize}

\noi
You are right. 
We now introduce this abbreviation the first time we use the term `confidence interval' in the introduction. 
From this point on, we use the abbreviated form `CI' throughout the paper, except for Section 4.5 title (Asymptotic Validity of the Confidence Intervals). 
\medskip

### 2014-06-09 omrp_lb_rev.tex
More Referee 2 suggestions
Changes in the response to Referee 2 as well as the paper itself

Computing the above optimality gap estimate involves solving an optimization problem (\ref{eq:sto_prog_m}) to obtain a lower bound estimator of $\zs$, $\zs_m$, which complicates the statistical analysis. 
As mentioned above, to enable statistical inference, the MRP of \citet{Mak1999} generates $k$ independent estimators, each using sample size $m$ ($k$ nonoverlapping batches of size $m$) and averages them to obtain a point estimator.  
The sample variance of these estimators is used to form confidence intervals for the optimality gap (we further review MRP in \S \ref{ssec:mrp}).  
An advantage of MRP is its applicability to a wide range of problems.  
With i.i.d.\ sampling, $f$ can be linear or nonlinear, $\X$ can include integrality constraints or not.  
It is also easy to implement; thus, MRP has been applied to a wide variety of problems, including finance, supply chain network design, etc.; see, e.g., \citep{bertocchi_etal_99,janjarassuk_linderoth_08,santoso_ahmed_etal_05}.  
Recently, the approach of (nonoverlapping) batching has been used for assessing solution quality of stochastic programs with finitely many expected value \citep{wang_ahmed_08} and stochastic dominance \citep{hu2010sample} constraints.

@@

Our aim is to apply the idea of overlapping batches to MRP.  
Overlapping could help to obtain better variance estimators with simple data reuse, resulting in improved confidence intervals.
%Especially for problems where sampling error is dominant, this simple data reuse method could yield better estimators.
We note several differences in this setting compared to the classical setting.  
In simulation output analysis, the point of interest is that of estimating the variance of the sample mean of a covariance stationary process.  
We are interested in estimating the variance of an optimality gap estimator.  
Notice that an optimality gap estimator not only has a sample mean $(\frac{1}{m} \sum_{i=1}^m f(\xh,\xiti))$ but also a minimized sample mean $(\zs_m)$.  
Minimization changes the statistical properties of sample means.  
For instance, the central limit theorem may not hold for a minimized sample mean, even though it holds for each $\x \in \X$.  
Therefore, analysis of the asymptotic benefits of overlapping becomes more complicated.
We overcome this technical difficulty by approximating the optimality gap estimators by their nonoptimized counterparts (see \S \ref{sec:theory}).  
The nonoptimized counterparts are (regular) overlapping batch means estimators (without any optimization present); therefore, they have the desired statistical properties of approximately the same bias and lower variances compared to their nonoverlapping versions. 
We establish convergence of the optimality gap estimators that use overlapping to their nonoptimized counterparts. 
Another difference between our setting and simulation output analysis is that once the data are generated through a simulation, it can be reused without much additional computational effort to obtain the OBM variance estimator.  
In this setting, due to the need to solve a sampling problem (SP$_m$), the computational effort may increase with data reuse.  
This can be alleviated in two ways. 
First, near-optimal variance reduction can be obtained by partially overlapping the batches \citep{Welch1987,Song1992}.  
Partial overlapping results in a smaller number of batches; hence, fewer optimization problems need to be solved.
In this paper, we consider variable amounts of overlap and examine this both theoretically and empirically. 
Second, in many solution methods, warm-starting can be used to quickly solve the sampling approximations with overlapping samples, considerably reducing solution time.

@@

The rest of the paper is organized as follows.  
In the next section, we review relevant background information.  
We first discuss overlapping batch means in \S \ref{ssec:obm} and then briefly go over MRP in \S \ref{ssec:mrp}.  
In \S \ref{sec:omrp}, we present the Overlapping Multiple Replications Procedure (OMRP) with a parametrized degree of overlap.  
In \S \ref{sec:theory}, we show strong consistency of the OMRP point estimators, asymptotic validity of the OMRP confidence intervals, and the variance reduction results as in the classical case.
In \S \ref{sec:comp}, we test the performance of OMRP on four problems and end in \S \ref{sec:concl} with a summary and conclusions.

@@

\subsection{Overlapping Batch Means} \label{ssec:obm}
Consider a covariance stationary stochastic process with mean $\mu$ and variance $\sigma^2$.  
The task is to estimate $\mu$ given some realization of the stochastic process $\y = (y^1, y^2, \dots, y^n)$.  
Typically, this involves forming a confidence interval of the form $[L_\alpha(\y), U_\alpha(\y)]$ for a given level of significance $\alpha$ such that $\p{L_\alpha(\y) \leq \mu \leq U_\alpha(\y)} = 1 - \alpha$ or that this probability is approximately $1 - \alpha$ for large enough sample sizes.  
The usual estimator for $\mu$ is the sample mean $\ybb = \frac{1}{n} \sum_{i=1}^n y^i$, which is an unbiased estimator even in the presence of correlated data.  
However, the usual variance estimator $\frac{1}{n-1} \sum_{i=1}^n (y^i - \ybb)^2$ can be inappropriate to use in the presence of correlated data, resulting in inaccurate interval estimators.  
To overcome this difficulty, various variance estimators have been proposed in the simulation literature; see, e.g., \citep{law_07}.  
We briefly review two of these variance estimators: nonoverlapping and overlapping batch means.

Nonoverlapping batch means takes $n$ observations, $y^1, \dots, y^n$ of the stochastic process and splits them into $k$ batches of size $m$, where $k = \frac{n}{m}$ (for simplicity, assume, for now, $n = mk$).  
The sample mean of each batch is then computed as
$
	\yb_j = \frac{1}{m} \sum_{i=1}^{m} y^{m(j-1)+i}, j = 1,2, \dots, k,
$
and the overall sample mean $\ybb = \frac{1}{k} \sum_{j=1}^k \yb_j = \frac{1}{n} \sum_{i=1}^n y^i$ provides a point estimator of $\mu$.  
The sample variance of the batch means is calculated as
\begin{equation} \label{eq:var}
	\varhat(\ybb) = \frac{m}{n}\frac{1}{k-1} \sum_{j=1}^k \left( \yb_j - \ybb \right)^2,
\end{equation}
and the $(1-\alpha)$-level approximate confidence interval (CI) is formed by $\ybb \pm t_{k-1,\alpha/2} \sqrt{\varhat(\ybb)}$, where $t_{k-1,\alpha/2}$ denotes the $1-\alpha/2$ quantile of the Student's t distribution with $k-1$ degrees of freedom.  
Under appropriate conditions, $n\varhat(\ybb)$ is a consistent estimator of $\sigma^2$.

@@

The sample variance estimator is updated to
\begin{equation} \label{eq:overlap_variance_def}
	\vart{\ybb} = \frac{1}{(\tfrac{n}{m}-1)(n - m + 1)}\sum_{j=1}^{n-m+1} (\yb_j(m) - \ybb)^2.
\end{equation}
Note that the corresponding batch means are no longer independent. 
However, by simply reusing the data in this fashion---and seemingly in a contradictory way that induces dependence---one obtains a better variance estimator. 
\citet{Meketon1984} show that: (i) the overlapping variance estimator has nearly the same bias as the standard nonoverlapping variance estimator, and (ii) the overlapping estimator has only two-thirds of the asymptotic variance of the nonoverlapping one.  
That is, 
\begin{equation} \label{eq:asym_var}
	\frac{ \var{\vart{\ybb}} }{ \var{\varhat(\ybb)} } \rightarrow \frac{2}{3}
\end{equation}
in the limit as batch size $m$ and the number of batches $(n/m)$ tend to infinity.  
Note that the degrees of freedom in (\ref{eq:overlap_variance_def}) is slightly different than in \citep{Meketon1984}.  
The degrees of freedom in (\ref{eq:overlap_variance_def}) makes $\vart{\ybb}$ an unbiased estimator for i.i.d.\ data for all finite $m$ and $n$ with the same asymptotic benefits \citep{Song1992}.  
The $(1-\alpha)$-level approximate CI is similarly formed by $\ybb \pm t_{3(k-1)/2,\alpha/2} \sqrt{\vart{\ybb}}$, with an adjustment to the degrees of freedom.

@@

Notice that the minimization in the second term on the right-hand side of (\ref{eq:mrp_gap}) gives rise to a biased gap estimator (recall the upper bound on the optimality gap).  
Thus, we can expect that the true probability of the optimality gap residing within the confidence interval to be greater than the $1 - \alpha$ suggested by the above calculation.  
This is shown empirically in \citep{Bayraksan2006}, which also investigates additional methods for using a smaller number of replications (e.g., 1 or 2) with an alternative variance estimator to compute a confidence interval.  
See also \citep{bayraksan_morton_09,partani2006jackknife,partani_07} for variations of MRP aimed to reduce bias and variance.

@@

The overlapping variance estimator for stochastic programs displays the same desirable properties as in simulation, but we must still check that it results in a valid confidence interval.  
Let $I^G_l = \gbb_l + t_{d_l,\alpha} \sqrt{VG_l}$ be the width of the one-sided confidence interval generated by OMRP. 
The degrees of freedom $d_l$ is the inverse of (\ref{eq:var_reduct_formula}) using $\frac{\gamma_l}{m_l}$ instead of $\gammab$.

@@

The asymptotic validity of the OMRP confidence interval requires $n_l VD_l$ to converge in probability to $\sigma^{2}_{\xh}$. 
This can be achieved either by almost sure or mean-square convergence, which gives a larger range of $r$ in the batching structure.
Also, a hypothesis of Theorem~\ref{thm:conf_int} is that $\xh \neq \xs$.  For $\xh = \xs$, we have $\lim_{l\rightarrow\infty} \p{\mu_\xh \leq I^G_l} = 1$.

@@

Our experiments were conducted as follows. 
We used a total sample size of $n = 30 m$, with several values of the batch size $m=100, 200, \ldots$. 
Then, at each value of $m$, we formed the OMRP estimators with varying amounts of overlap. 
We also set $\alpha=0.10$, forming 90\% confidence intervals on the optimality gap using the ORMP estimators. 
Results for NVD were compiled over 10,000 independent runs, while the CEP1 and 10D results were taken over 1,000 independent runs, and DB1 results were generated over 500 independent runs.

@@

\begin{figure}[htb!]
	\centering
	\subfloat[][Variance Reduction]{
	   \label{fig:nv_varvar}
	   \includegraphics[width=.32\textwidth]{images/nv_varvar_discrete}}
	\subfloat[][Expected Variance]{
	   \label{fig:nv_avgvar}
	   \includegraphics[width=.32\textwidth]{images/nv_avgvar_discrete}}
	\subfloat[][Coverage Probability]{
	   \label{fig:nv_cover}
	   \includegraphics[width=.32\textwidth]{images/nv_cover_discrete}}
	\caption{
		Summary of results for NVD. 
		(a) Reduction in variance of $nVG$,
		(b) estimates of $\e{nVG}$, and 
		(c) coverage probability of the confidence intervals for various values of $\gamma/m$ ($\gamma/m=1$ denotes the nonoverlapping batches).
	}
\label{fig:nv}
\end{figure}

@@

Finally, Figure~\ref{fig:nv}(c) shows the coverage probability of confidence intervals generated by OMRP for several values of $m$ across varying values of $\gamma/m$ for the newsvendor problem.  
The results of the classical overlapping batches estimators show that coverage probability does not change with the amount of overlap, which we can  empirically see in this figure for OMRP for NVD.
We observed the same for CEP1, 10D, and DB1.  
The coverage probabilities from applying the (nonoverlapping) MRP algorithm to these problems presented in \citep{Bayraksan2006} agree with our results: for the newsvendor problem, coverage probability drops as $m$ increases and the coverage probability of CEP1 (not shown) remains fairly constant around the desired value of $90\%$. 
Coverage probability for 10D (not shown) and {\it estimated} coverage probability for DB1 (also not shown) were very high, more than $0.99$.  
The bias from solving (\ref{eq:sto_prog_m}) for these problems seems to be much more significant than the variance.

@@

We have extended previous work from simulation output analysis to assessing solution quality in stochastic programming by means of variably overlapping batches \citep{Meketon1984,Song1992,Welch1987} for Monte Carlo simulation-based estimators of optimality gaps in stochastic programs \citep{Mak1999}. 
We have provided conditions under which the resulting point estimator of the optimality gap and its associated sample variance are consistent, the same variance reduction can be achieved, and asymptotically valid confidence intervals can be formed. 
Empirical results with small sample sizes indicate that the asymptotic reductions in variance of the variance estimator show a similar decrease in OMRP, while bias and coverage probability remain unaffected.

>>>>

Computing the above optimality gap estimate involves solving an optimization problem (\ref{eq:sto_prog_m}) to obtain a lower bound estimator of $\zs$, $\zs_m$, which complicates the statistical analysis. 
As mentioned above, to enable statistical inference, the MRP of \citet{Mak1999} generates $k$ independent estimators, each using sample size $m$ ($k$ nonoverlapping batches of size $m$) and averages them to obtain a point estimator.  
The sample variance of these estimators is used to form confidence intervals (CIs) for the optimality gap (we further review MRP in \S \ref{ssec:mrp}).  
An advantage of MRP is its applicability to a wide range of problems.  
With i.i.d.\ sampling, $f$ can be linear or nonlinear, $\X$ can include integrality constraints or not.  
It is also easy to implement; thus, MRP has been applied to a wide variety of problems, including finance, supply chain network design, etc.; see, e.g., \citep{bertocchi_etal_99,janjarassuk_linderoth_08,santoso_ahmed_etal_05}.  
Recently, the approach of (nonoverlapping) batching has been used for assessing solution quality of stochastic programs with finitely many expected value \citep{wang_ahmed_08} and stochastic dominance \citep{hu2010sample} constraints.

@@

Our aim is to apply the idea of overlapping batches to MRP.  
Overlapping could help to obtain better variance estimators with simple data reuse, resulting in improved CIs.
%Especially for problems where sampling error is dominant, this simple data reuse method could yield better estimators.
We note several differences in this setting compared to the classical setting.  
In simulation output analysis, the point of interest is that of estimating the variance of the sample mean of a covariance stationary process.  
We are interested in estimating the variance of an optimality gap estimator.  
Notice that an optimality gap estimator not only has a sample mean $(\frac{1}{m} \sum_{i=1}^m f(\xh,\xiti))$ but also a minimized sample mean $(\zs_m)$.  
Minimization changes the statistical properties of sample means.  
For instance, the central limit theorem may not hold for a minimized sample mean, even though it holds for each $\x \in \X$.  
Therefore, analysis of the asymptotic benefits of overlapping becomes more complicated.
We overcome this technical difficulty by approximating the optimality gap estimators by their nonoptimized counterparts (see \S \ref{sec:theory}).  
The nonoptimized counterparts are (regular) overlapping batch means estimators (without any optimization present); therefore, they have the desired statistical properties of approximately the same bias and lower variances compared to their nonoverlapping versions. 
We establish convergence of the optimality gap estimators that use overlapping to their nonoptimized counterparts. 
Another difference between our setting and simulation output analysis is that once the data are generated through a simulation, it can be reused without much additional computational effort to obtain the OBM variance estimator.  
In this setting, due to the need to solve a sampling problem (SP$_m$), the computational effort may increase with data reuse.  
This can be alleviated in two ways. 
First, near-optimal variance reduction can be obtained by partially overlapping the batches \citep{Welch1987,Song1992}.  
Partial overlapping results in a smaller number of batches; hence, fewer optimization problems need to be solved.
In this paper, we consider variable amounts of overlap and examine this both theoretically and empirically. 
Second, in many solution methods, warm-starting can be used to quickly solve the sampling approximations with overlapping samples, considerably reducing solution time.

@@

The rest of the paper is organized as follows.  
In the next section, we review relevant background information.  
We first discuss overlapping batch means in \S \ref{ssec:obm} and then briefly go over MRP in \S \ref{ssec:mrp}.  
In \S \ref{sec:omrp}, we present the Overlapping Multiple Replications Procedure (OMRP) with a parametrized degree of overlap.  
In \S \ref{sec:theory}, we show strong consistency of the OMRP point estimators, asymptotic validity of the OMRP CIs, and that the OMRP variance estimators have lower variances than their nonoverlapping counterparts---the MRP estimators.
In \S \ref{sec:comp}, we test the performance of OMRP on four problems and end in \S \ref{sec:concl} with a summary and conclusions.

@@

\subsection{Overlapping Batch Means} \label{ssec:obm}
Consider a covariance stationary stochastic process with mean $\mu$ and variance $\sigma^2$.  
The task is to estimate $\mu$ given some realization of the univariate stochastic process $\y = (y^1, y^2, \dots, y^n)$.  
Typically, this involves forming a CI of the form $[L_\alpha(\y), U_\alpha(\y)]$ for a given level of significance $\alpha$ such that $\p{L_\alpha(\y) \leq \mu \leq U_\alpha(\y)} = 1 - \alpha$ or that this probability is approximately $1 - \alpha$ for large enough sample sizes.  
The usual estimator for $\mu$ is the sample mean $\ybb = \frac{1}{n} \sum_{i=1}^n y^i$, which is an unbiased estimator even in the presence of correlated data.  
However, the usual variance estimator $\frac{1}{n-1} \sum_{i=1}^n (y^i - \ybb)^2$ can be inappropriate to use in the presence of correlated data, resulting in inaccurate interval estimators.  
To overcome this difficulty, various variance estimators have been proposed in the simulation literature; see, e.g., \citep{law_07}.  
We briefly review two of these variance estimators: nonoverlapping and overlapping batch means.

Nonoverlapping batch means takes $n$ observations, $y^1, \dots, y^n$ of the stochastic process and splits them into $k$ batches of size $m$, where $k = \frac{n}{m}$ (for simplicity, assume, for now, $n = mk$).  
The sample mean of each batch is then computed as
$
	\yb_j = \frac{1}{m} \sum_{i=1}^{m} y^{m(j-1)+i}, j = 1,2, \dots, k,
$
and the overall sample mean $\ybb = \frac{1}{k} \sum_{j=1}^k \yb_j = \frac{1}{n} \sum_{i=1}^n y^i$ provides a point estimator of $\mu$.  
The variance estimator of the batch means, which is $n/m$ times the sample variance, is calculated as
\begin{equation} \label{eq:var}
	\varhat(\ybb) = \frac{m}{n}\frac{1}{k-1} \sum_{j=1}^k \left( \yb_j - \ybb \right)^2.
\end{equation}
The $(1-\alpha)$-level approximate CI is then formed by $\ybb \pm t_{k-1,\alpha/2} \sqrt{\varhat(\ybb)}$, where $t_{k-1,\alpha/2}$ denotes the $1-\alpha/2$ quantile of the Student's t distribution with $k-1$ degrees of freedom.  
Under appropriate conditions, $n\varhat(\ybb)$ is a consistent estimator of $\sigma^2$.

@@

The sample variance estimator is updated to
\begin{equation} \label{eq:overlap_variance_def}
	\vart{\ybb} = \frac{1}{(\tfrac{n}{m}-1)(n - m + 1)}\sum_{j=1}^{n-m+1} (\yb_j(m) - \ybb)^2.
\end{equation}
Note that the corresponding overlapping batch means are no longer independent. 
However, by simply reusing the data in this fashion---and seemingly in a contradictory way that induces dependence---one obtains a better variance estimator. 
\citet{Meketon1984} show that: (i) the overlapping variance estimator has nearly the same bias as the standard nonoverlapping variance estimator, and (ii) the overlapping estimator has only two-thirds of the asymptotic variance of the nonoverlapping one.  
That is, 
\begin{equation} \label{eq:asym_var}
	\frac{ \var{\vart{\ybb}} }{ \var{\varhat(\ybb)} } \rightarrow \frac{2}{3}
\end{equation}
in the limit as batch size $m$ and the number of batches $(n/m)$ tend to infinity.  
Note that the degrees of freedom in (\ref{eq:overlap_variance_def}) is slightly different than in \citep{Meketon1984}.  
The degrees of freedom in (\ref{eq:overlap_variance_def}) makes $\vart{\ybb}$ an unbiased estimator for i.i.d.\ data for all finite $m$ and $n$ with the same asymptotic benefits \citep{Song1992}.  
The $(1-\alpha)$-level approximate CI is similarly formed by $\ybb \pm t_{3(k-1)/2,\alpha/2} \sqrt{\vart{\ybb}}$, with an adjustment to the degrees of freedom.

@@

Notice that the minimization in the second term on the right-hand side of (\ref{eq:mrp_gap}) gives rise to a biased gap estimator (recall the upper bound on the optimality gap).  
Thus, we can expect that the true probability of the optimality gap residing within the CI to be greater than the $1 - \alpha$ suggested by the above calculation.  
This is shown empirically in \citep{Bayraksan2006}, which also investigates additional methods for using a smaller number of replications (e.g., 1 or 2) with an alternative variance estimator to compute a CI.  
See also \citep{bayraksan_morton_09,partani2006jackknife,partani_07} for variations of MRP aimed to reduce bias and variance.

@@

The overlapping variance estimator for stochastic programs displays the same desirable properties as in simulation, but we must still check that it results in a valid CI.  
Let $I^G_l = \gbb_l + t_{d_l,\alpha} \sqrt{VG_l}$ be the width of the one-sided CI generated by OMRP. 
The degrees of freedom $d_l$ is the inverse of (\ref{eq:var_reduct_formula}) using $\frac{\gamma_l}{m_l}$ instead of $\gammab$.

@@

The asymptotic validity of the OMRP CI requires $n_l VD_l$ to converge in probability to $\sigma^{2}_{\xh}$. 
This can be achieved either by almost sure or mean-square convergence, which gives a larger range of $r$ in the batching structure.
Also, a hypothesis of Theorem~\ref{thm:conf_int} is that $\xh \neq \xs$.  For $\xh = \xs$, we have $\lim_{l\rightarrow\infty} \p{\mu_\xh \leq I^G_l} = 1$.

@@

Our experiments were conducted as follows. 
We used a total sample size of $n = 30 m$, with several values of the batch size $m=100, 200, \ldots$. 
Then, at each value of $m$, we formed the OMRP estimators with varying amounts of overlap. 
We also set $\alpha=0.10$, forming 90\% CIs on the optimality gap using the ORMP estimators. 
Results for NVD were compiled over 10,000 independent runs, while the CEP1 and 10D results were taken over 1,000 independent runs, and DB1 results were generated over 500 independent runs.

@@

\begin{figure}[htb!]
	\centering
	\subfloat[][Variance Reduction]{
	   \label{fig:nv_varvar}
	   \includegraphics[width=.32\textwidth]{images/nv_varvar_discrete}}
	\subfloat[][Expected Variance]{
	   \label{fig:nv_avgvar}
	   \includegraphics[width=.32\textwidth]{images/nv_avgvar_discrete}}
	\subfloat[][Coverage Probability]{
	   \label{fig:nv_cover}
	   \includegraphics[width=.32\textwidth]{images/nv_cover_discrete}}
	\caption{
		Summary of results for NVD. 
		(a) Reduction in variance of $nVG$,
		(b) estimates of $\e{nVG}$, and 
		(c) coverage probability of the CIs for various values of $\gamma/m$ ($\gamma/m=1$ denotes the nonoverlapping batches).
	}
\label{fig:nv}
\end{figure}

@@

Finally, Figure~\ref{fig:nv}(c) shows the coverage probability of CIs generated by OMRP for several values of $m$ across varying values of $\gamma/m$ for the newsvendor problem.  
The results of the classical overlapping batches estimators show that coverage probability does not change with the amount of overlap, which we can  empirically see in this figure for OMRP for NVD.
We observed the same for CEP1, 10D, and DB1.  
The coverage probabilities from applying the (nonoverlapping) MRP algorithm to these problems presented in \citep{Bayraksan2006} agree with our results: for the newsvendor problem, coverage probability drops as $m$ increases and the coverage probability of CEP1 (not shown) remains fairly constant around the desired value of $90\%$. 
Coverage probability for 10D (not shown) and {\it estimated} coverage probability for DB1 (also not shown) were very high, more than $0.99$.  
The bias from solving (\ref{eq:sto_prog_m}) for these problems seems to be much more significant than the variance.

@@

We have extended previous work from simulation output analysis to assessing solution quality in stochastic programming by means of variably overlapping batches \citep{Meketon1984,Song1992,Welch1987} for Monte Carlo simulation-based estimators of optimality gaps in stochastic programs \citep{Mak1999}. 
We have provided conditions under which the resulting point estimator of the optimality gap and its associated sample variance are consistent, the same variance reduction can be achieved, and asymptotically valid CIs can be formed. 
Empirical results with small sample sizes indicate that the asymptotic reductions in variance of the variance estimator show a similar decrease in OMRP, while bias and coverage probability remain unaffected.
